---
title: "Coursera - Statistical Inference"
author: "Teddy Rusli"
date: "Friday, May 21, 2015"
output: html_document
---

This project is meant to show how exponential distribution compared with the Central Limit Theorem. The exponential distribution is simulated with rexp(n,lambda) where lambda is the rate parameter. Lambda = 0.2 is set for all the simulations

Step 1: Show the sample mean and compare it to the theoretical mean of the distribution.

```{r}
library(ggplot2)

lambda <- 0.2
n <- 40
simNumber <- 1:1000
set.seed(888)

sampleMean <- data.frame(
                x = sapply(simNumber, 
                    function(x) {
                        mean(rexp(n,rate = lambda))
                    }
                    )
                )

simMean <- mean(sampleMean$x)
trueMean <- 1/lambda

```

The simulation resulted in a sample mean of `r simMean` and theoratical mean is `r trueMean`. 


2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

```{r}

simVar <- var(sampleMean$x)
trueVar <- ((1/lambda)/sqrt(n))^2
```

The simulation resulted in a sample mean of `r simVar` and theoratical mean is `r trueVar`. 


3. Show that the distribution is approximately normal.

```{r}
ggplot(data = sampleMean, aes(x = x)) + 
    geom_histogram(aes(y=..density..),binwidth = 0.10) +
    stat_function(fun = dnorm, arg = list(mean = trueMean, sd = sd(sampleMean$x)))
```

The plot compares the distribution of the means from the simulation against a normal distribution.  We can conclude that the Central Limit Theorem applies on exponential distribution

